Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-18 sports_analytics.Rmd
eval chess chunk based on username

```{r chess, fig.show="hold", out.width="49%", fig.cap="At left, the starting chess board printed via the \\pkg{chess} package. At right, the final position for one of the authors' recent wins (a checkmate playing Black)."}
# library(chess)
# # Sys.setenv(RETICULATE_PYTHON = "my_env/bin/python3")
# game() |> plot()
# 
# library(chessR)
# us <- c("fatgreggy")
# greg <- get_raw_chessdotcom(
#   usernames = us,
#   year_month = 202206
# )
# 
# m <- extract_moves_as_game(greg[6, ])
# # plot_moves(m, interactive = FALSE)
# plot(m)
```

>>>>

```{r chess, eval=whoami::username() == 'bbaumer', fig.show="hold", out.width="49%", fig.cap="At left, the starting chess board printed via the \\pkg{chess} package. At right, the final position for one of the authors' recent wins (a checkmate playing Black)."}
library(chess)
# Sys.setenv(RETICULATE_PYTHON = "my_env/bin/python3")
game() |> plot()

library(chessR)
us <- c("fatgreggy")
greg <- get_raw_chessdotcom(
  usernames = us,
  year_month = 202206
)

m <- extract_moves_as_game(greg[6, ])
# plot_moves(m, interactive = FALSE)
plot(m)
```
